Synthesizing Verified Components~~~\\ for Cyber Assured Systems Engineering~ \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2021-08-01 paper/case-study.tex
Slight wordsmithing

In this section, we outline the application of the BriefCASE tool towards the development of a UAV surveillance system as a part of the DARPA CASE program.
The motivation was to showcase the toolchain on an industrial scale problem, to see if the technology works, i.e. provides engineers with early validation of their model; provides early information about cyber-vulnerabilities and in the effectiveness of related mitigations; to show that the tool can handle the UXAS message format (a complex, real-world message format); and to validate the utility and capability of the toolchain.

>>>>

In this section, we outline the application of the BriefCASE tool towards the development of a UAV surveillance system as a part of the DARPA CASE program.
The motivation was to showcase the utility and capability of the BriefCASE toolchain on an industrial scale problem, to determine whether the technology provides engineers with early validation of their model; produces early information about cyber-vulnerabilities; provides effective mitigations; and handles a complex real-world message format, namely  the UxAS message format.
